---
title: "MIXOMICS - R WORKSHOP - MACQUARIE UNIVERSITY"
author: "Pat Buerger (patrick.buerger@mq.edu.au)"
date: '07-09-2023'
output:
  pdf_document:
    extra_dependencies: subfig
    number_sections: yes
    toc: yes
    toc_depth: 3
    highlight: zenburn
header-includes:
- \usepackage{fancyhdr}
- \usepackage{mathtools}
- \usepackage{hyperref}
- \setlength{\headheight}{33pt}
- \setlength{\footskip}{25pt}
- \pagestyle{fancy}
- \renewcommand{\headrulewidth}{0.5pt}
- \renewcommand{\footrulewidth}{0.5pt}
- \rhead{\thepage}
- \hypersetup{colorlinks   = true, linkcolor=blue, urlcolor  = blue}
- \fancypagestyle{plain}{\pagestyle{fancy}}
editor_options:
  chunk_output_type: console
---

```{r global_options, include=FALSE}
library(knitr)
# global options to show by default the code, dump the figures into /Figures etc
# change as required
knitr::opts_chunk$set(dpi = 100, 
                      echo=TRUE, 
                      warning=FALSE, message=FALSE, eval = TRUE,
                      fig.show=TRUE, fig.width= 6,fig.height= 5,fig.align='center', 
                      out.width = '60%', fig.path= 'Figures/')
```
<br>

###############################################################
###############################################################
# INTRODUCTION
###############################################################
<p>Abstract: </p>
MixOmics example: Case Study of DIABLO with Breast TCGA Dataset, using PCA, PLS-DA (supervised), sparse PLS-DA (supervised + data reduction), and multiblock sparse PLS-DA (DIABLO).
<p> **Modified code from MixOmics R package** </p>
Source for R-code: https://mixomicsteam.github.io/mixOmics-Vignette/

## Load Packages
```{r packages, message=FALSE}
#install.packages('markdown')
#install.packages('mixOmics')
#install.packages('tidyverse')
library(mixOmics)
library(tidyverse)

```
\

## Load Data
```{r}
# Load data
data(breast.TCGA)

# Extract training data and name each data frame
# Store as list
X <- list(mRNA = breast.TCGA$data.train$mrna, 
          miRNA = breast.TCGA$data.train$mirna, 
          protein = breast.TCGA$data.train$protein)

# Outcome
Y <- breast.TCGA$data.train$subtype
summary(Y)
```

<!-- New page -->     
\pagebreak

###############################################################
###############################################################
# Principal Component Analysis (PCA)
###############################################################
```{r}
# Check data first with PCA to detect outliers and general structure of data.
# 1 Run the method
MyResult.pca_miRNA <- pca(X$miRNA)  

MyResult.pca_mRNA <- pca(X$mRNA)  

MyResult.pca_protein <- pca(X$protein)

```

```{r}
## 2.1 Plot the samples
## miRNA
# PLOT WITH ADDITIONAL SYMBOLS
plotIndiv(MyResult.pca_miRNA, ind.names = FALSE,
          group = Y,
          pch = as.factor(Y), 
          legend = TRUE, title = 'miRNA: PCA comp 1 - 2',
          legend.title = 'miRNA', legend.title.pch = 'miRNA')
```
<p style="text-align: center;">**FIGURE: miRNA PCA:** comp 1 - 2</p>
<br>
<br>

```{r}
## 2.2 Plot the samples
## mRNA
# PLOT WITH ADDITIONAL SYMBOLS
plotIndiv(MyResult.pca_mRNA, ind.names = FALSE,
          group = Y,
          pch = as.factor(Y), 
          legend = TRUE, title = 'mRNA: PCA comp 1 - 2',
          legend.title = 'mRNA', legend.title.pch = 'mRNA')
```
<p style="text-align: center;">**FIGURE: mRNA PCA:** comp 1 - 2</p>
<br>
<br>

```{r}
## 2.3 Plot the samples
## protein
# PLOT WITH ADDITIONAL SYMBOLS
plotIndiv(MyResult.pca_protein, ind.names = FALSE,
          group = Y,
          pch = as.factor(Y), 
          legend = TRUE, title = 'protein: PCA comp 1 - 2',
          legend.title = 'protein', legend.title.pch = 'protein')
```
<p style="text-align: center;">**FIGURE: protein PCA:** comp 1 - 2</p>
<br>
<br>

#### PCA: Conclusion
Data looks all right. No outliers detected. Seems to be some grouping of samples present. <br>
-> Problem: There is some source of variation in the data that we can not explain with our strain groupings. <br>
-> We need to have some sort of supervised analysis to resolve this. <br>
<br>


###############################################################
###############################################################
# Partial Least Squares – Discriminant Analysis (PLS-DA)
###############################################################
```{r}
##### PLS-DA, sPLS-DA ####
# 1 Run the method
MyResult.plsda_miRNA <- plsda(X$miRNA, Y)  

MyResult.plsda_mRNA <- plsda(X$mRNA, Y)  

MyResult.plsda_protein <- plsda(X$protein, Y)
```

```{r}
# sPLS-DA NEEDS TO BE TUNED AND NUMBERS OF COMPONENTS OPTIMISED. SKIPPED HERE DUE TO TIME CONSTRAINTS. SEE LINK BELOW FOR FURTHER INFORMATION:
#https://mixomicsteam.github.io/mixOmics-Vignette/id_05.html

# 2.1 Plot the samples
plotIndiv(MyResult.plsda_miRNA, ind.names = FALSE,
          group = Y,
          pch = as.factor(Y), 
          legend = TRUE, title = 'miRNA: PLS-DA comp 1 - 2',
          legend.title = 'miRNA', legend.title.pch = 'miRNA')
```
<p style="text-align: center;">**FIGURE: miRNA PLS-DA:** comp 1 - 2, supervised analysis using the full data.</p>
<br>
<br>

```{r}
# sPLS-DA NEEDS TO BE TUNED AND NUMBERS OF COMPONENTS OPTIMISED. SKIPPED HERE DUE TO TIME CONSTRAINTS. SEE LINK BELOW FOR FURTHER INFORMATION:
#https://mixomicsteam.github.io/mixOmics-Vignette/id_05.html

# 2.2 Plot the samples
plotIndiv(MyResult.plsda_mRNA, ind.names = FALSE,
          group = Y,
          pch = as.factor(Y), 
          legend = TRUE, title = 'mRNA: PLS-DA comp 1 - 2',
          legend.title = 'mRNA', legend.title.pch = 'mRNA')

```
<p style="text-align: center;">**FIGURE: mRNA PLS-DA:** comp 1 - 2, supervised analysis using the full data.</p>
<br>
<br>

```{r}
# sPLS-DA NEEDS TO BE TUNED AND NUMBERS OF COMPONENTS OPTIMISED. SKIPPED HERE DUE TO TIME CONSTRAINTS. SEE LINK BELOW FOR FURTHER INFORMATION:
#https://mixomicsteam.github.io/mixOmics-Vignette/id_05.html

# 2.3 Plot the samples
plotIndiv(MyResult.plsda_protein, ind.names = FALSE,
          group = Y,
          pch = as.factor(Y), 
          legend = TRUE, title = 'protein: PLS-DA comp 1 - 2',
          legend.title = 'protein', legend.title.pch = 'protein')

```
<p style="text-align: center;">**FIGURE: protein PLS-DA:** comp 1 - 2, supervised analysis using the full data.</p>
<br>
<br>


```{r}
# 3.1 Plot the variables
plotVar(MyResult.plsda_miRNA)              
```
<p style="text-align: center;">**FIGURE: miRNA: PLS-DA:** contributing variables to PLS-DA comp 1 - 2, supervised analysis using the full data.</p>
<br>
<br>

```{r}
# 3.2 Plot the variables
plotVar(MyResult.plsda_mRNA)              
```
<p style="text-align: center;">**FIGURE: mRNA: PLS-DA:** contributing variables to PLS-DA comp 1 - 2, supervised analysis using the full data.</p>
<br>
<br>

```{r}
# 3.3 Plot the variables
plotVar(MyResult.plsda_protein)              
```
<p style="text-align: center;">**FIGURE: Protein: PLS-DA:** contributing variables to PLS-DA comp 1 - 2, supervised analysis using the full data.</p>
<br>
<br>

#### PLS-DA: Conclusion
Lots of variable and some noise in the data. Data reduction might be beneficial using a sparse PLS-DA in order to separate groups and get a clear picture of the data and important variables. 
<br>
<br>
<br>

<!-- New page -->     
\pagebreak

###############################################################
###############################################################
# sparse Partial Least Squares – Discriminant Analysis (sPLS-DA)
###############################################################
```{r}
# DATA REDUCTION APPROACH.
#########
# miRNA
#########

# sPLS-DA NEEDS TO BE TUNED AND NUMBERS OF COMPONENTS OPTIMISED. SKIPPED HERE DUE TO TIME CONSTRAINTS. SEE LINK BELOW FOR FURTHER INFORMATION:
#https://mixomicsteam.github.io/mixOmics-Vignette/id_05.html

#### sPLS-DA, using reduced data, TOP 15 variables
MyResult.splsda.miRNA <- splsda(X$miRNA, Y, keepX = c(15,15)) # 1 Run the method

plotIndiv(MyResult.splsda.miRNA)                   # 2 Plot the samples
```
<p style="text-align: center;">**FIGURE: miRNA sparse PLS-DA:** comp 1 - 2, supervised analysis using the only the most influential variables, here TOP 15.</p>
<br>
<br>

```{r}
plotVar(MyResult.splsda.miRNA)                     # 3 Plot the variables
```
<p style="text-align: center;">**FIGURE: miRNA contributing variables to sparse PLS-DA:** comp 1 - 2, supervised analysis using the only the most influential variables, here TOP 15.</p>
<br>
<br>

```{r}
selectVar(MyResult.splsda.miRNA, comp = 1)$value         # Selected variables on comp 1

plotLoadings(MyResult.splsda.miRNA, comp = 1, method = 'mean', contrib = 'max')
```
<p style="text-align: center;">**FIGURE: miRNA contributing variables to sparse PLS-DA:** comp 1.</p>
<br>
<br>

```{r}
selectVar(MyResult.splsda.miRNA, comp = 2)$value         # Selected variables on comp 1

plotLoadings(MyResult.splsda.miRNA, comp = 2, method = 'mean', contrib = 'max')
```
<p style="text-align: center;">**FIGURE: miRNA contributing variables to sparse PLS-DA:** comp 2.</p>
<br>
<br>

```{r}
# DATA REDUCTION APPROACH.
#########
# mRNA
#########

# sPLS-DA NEEDS TO BE TUNED AND NUMBERS OF COMPONENTS OPTIMISED. SKIPPED HERE DUE TO TIME CONSTRAINTS. SEE LINK BELOW FOR FURTHER INFORMATION:
#https://mixomicsteam.github.io/mixOmics-Vignette/id_05.html


#### sPLS-DA, using reduced data, TOP 15 variables
MyResult.splsda.mRNA <- splsda(X$mRNA, Y, keepX = c(15,15)) # 1 Run the method

plotIndiv(MyResult.splsda.mRNA)                   # 2 Plot the samples
```
<p style="text-align: center;">**FIGURE: mRNA sparse PLS-DA:** comp 1 - 2, supervised analysis using the only the most influential variables, here TOP 15.</p>
<br>
<br>

```{r}
plotVar(MyResult.splsda.mRNA)                     # 3 Plot the variables
```
<p style="text-align: center;">**FIGURE: mRNA contributing variables to sparse PLS-DA:** comp 1 - 2, supervised analysis using the only the most influential variables, here TOP 15.</p>
<br>
<br>

```{r}
selectVar(MyResult.splsda.mRNA, comp = 1)$value         # Selected variables on comp 1

plotLoadings(MyResult.splsda.mRNA, comp = 1, method = 'mean', contrib = 'max')
```
<p style="text-align: center;">**FIGURE: mRNA contributing variables to sparse PLS-DA:** comp 1.</p>
<br>
<br>

```{r}
selectVar(MyResult.splsda.mRNA, comp = 2)$value         # Selected variables on comp 1

plotLoadings(MyResult.splsda.mRNA, comp = 2, method = 'mean', contrib = 'max')
```
<p style="text-align: center;">**FIGURE: mRNA contributing variables to sparse PLS-DA:** comp 2.</p>
<br>
<br>


```{r}
# DATA REDUCTION APPROACH.
#########
# Protein
#########

# sPLS-DA NEEDS TO BE TUNED AND NUMBERS OF COMPONENTS OPTIMISED. SKIPPED HERE DUE TO TIME CONSTRAINTS. SEE LINK BELOW FOR FURTHER INFORMATION:
#https://mixomicsteam.github.io/mixOmics-Vignette/id_05.html

#### sPLS-DA, using reduced data, TOP 15 variables
MyResult.splsda.protein <- splsda(X$protein, Y, keepX = c(15,15)) # 1 Run the method

plotIndiv(MyResult.splsda.protein)                   # 2 Plot the samples
```
<p style="text-align: center;">**FIGURE: Protein sparse PLS-DA:** comp 1 - 2, supervised analysis using the only the most influential variables, here TOP 15.</p>
<br>
<br>

```{r}
plotVar(MyResult.splsda.protein)                     # 3 Plot the variables
```
<p style="text-align: center;">**FIGURE: Protein contributing variables to sparse PLS-DA:** comp 1 - 2, supervised analysis using the only the most influential variables, here TOP 15.</p>
<br>
<br>

```{r}
selectVar(MyResult.splsda.protein, comp = 1)$value         # Selected variables on comp 1

plotLoadings(MyResult.splsda.protein, comp = 1, method = 'mean', contrib = 'max')
```
<p style="text-align: center;">**FIGURE: Protein contributing variables to sparse PLS-DA:** comp 1.</p>
<br>
<br>

```{r}
selectVar(MyResult.splsda.protein, comp = 2)$value         # Selected variables on comp 1

plotLoadings(MyResult.splsda.protein, comp = 2, method = 'mean', contrib = 'max')
```
<p style="text-align: center;">**FIGURE: Protein contributing variables to sparse PLS-DA:** comp 2.</p>
<br>
<br>

#### sPLS-DA: Conclusion
Data reduction seems beneficial using a sparse PLS-DA in order to separate groups and get a clear picture of the data and important variables. Lets try the integrated data analysis using all three data sets.
<br>
<br>
<br>

<!-- New page -->     
\pagebreak

###############################################################
###############################################################
# Multiblock PLS-DA (DIABLO)
###############################################################
## Parameter choice
### Design matrix
```{r}
# HERE WE LOOK AT DESIGN MATRIX WITH 0.1.
# A full design with weights = 1 will favour the latter, but at the expense of classification accuracy, whereas a design with small weights will lead to a highly predictive signature. 
# FOR A FULLY WEIGHTED DESIGN: use "matrix(1, ncol...", WHICH IS FOCUSSING ON EXTRACTING THE MOST CORRELATION BETWEEN DATA SETS
design <- matrix(0.1, ncol = length(X), nrow = length(X), 
                dimnames = list(names(X), names(X)))
diag(design) <- 0
design 

## ---- results='hold'---------------------------------
# How much correlation between data sets?
pls.res1 <- pls(X$mRNA, X$protein, ncomp = 1)
cor(pls.res1$variates$X, pls.res1$variates$Y)

pls.res2 <- pls(X$mRNA, X$miRNA, ncomp = 1)
cor(pls.res2$variates$X, pls.res2$variates$Y)

pls.res3 <- pls(X$protein, X$miRNA, ncomp = 1)
cor(pls.res3$variates$X, pls.res3$variates$Y)
# Decent amount of correlation between data sets. The data sets taken in a pairwise manner are highly correlated, indicating that a design with weights could be chosen.
```

### Number of components
```{r}
## ----diablo-perf, message=FALSE, fig.cap='(ref:diablo-perf)'----
diablo.tcga <- block.plsda(X, Y, ncomp = 5, design = design)

set.seed(123) # For reproducibility, remove for your analyses
perf.diablo.tcga = perf(diablo.tcga, validation = 'Mfold', folds = 5, nrepeat = 5)
# The validation of the folds parameter was too high and had to be reduced.

# Plot of the error rates based on weighted vote
plot(perf.diablo.tcga)
```
<p style="text-align: center;">**FIGURE: Multi block PLS-DA, error rates:** based on weighted vote. Choosing the number of components. Error rate is minimum using how many dimensions? </p>
<br>
<br>

```{r}
## ----------------------------------------------------
perf.diablo.tcga$choice.ncomp$WeightedVote

## ----------------------------------------------------
ncomp <- perf.diablo.tcga$choice.ncomp$WeightedVote["Overall.BER", "centroids.dist"]
```


### Number of variables to select
```{r}
## ---- echo = FALSE, eval = TRUE, warning=FALSE-------
# chunk takes about 2 min to run
set.seed(123) # for reproducibility
test.keepX <- list(mRNA = c(5:9, seq(10, 25, 5)),
                   miRNA = c(5:9, seq(10, 20, 2)),
                   proteomics = c(seq(5, 25, 5)))

tune.diablo.tcga <- tune.block.splsda(X, Y, ncomp = 2, 
                              test.keepX = test.keepX, design = design,
                              validation = 'Mfold', folds = 2, nrepeat = 1, 
                              # use two CPUs for faster computation
                              BPPARAM = BiocParallel::SnowParam(workers = 2),
                              dist = "centroids.dist")


## ----------------------------------------------------
list.keepX <- tune.diablo.tcga$choice.keepX
list.keepX
```


## Final model
```{r}
## ---- message = TRUE---------------------------------
diablo.tcga <- block.splsda(X, Y, ncomp = ncomp, 
                          keepX = list.keepX, design = design)
#diablo.tcga   # Lists the different functions of interest related to that object

## ----------------------------------------------------
diablo.tcga$design

## ---- eval = FALSE-----------------------------------
## # mRNA variables selected on component 1
## selectVar(diablo.tcga, block = 'mRNA', comp = 1)
```


## Sample plots
### plotDiablo
```{r}
## variables selected on component 1
selectVar(diablo.tcga, block = 'miRNA', comp = 1)$miRNA$name
selectVar(diablo.tcga, block = 'mRNA', comp = 1)$mRNA$name
selectVar(diablo.tcga, block = 'protein', comp = 1)$protein$name

## ----plot-diablo, message=FALSE, fig.cap='(ref:plot-diablo)'----
plotDiablo(diablo.tcga, ncomp = 1)
```
<p style="text-align: center;">**FIGURE: Multi block PLS-DA, diagnostic plot:** component 1, 95% confidence intervals are plotted. Numbers indicate correlation coefficients between the first components from each data set.</p>
<br>
<br>

```{r}
## variables selected on component 1
selectVar(diablo.tcga, block = 'miRNA', comp = 2)$miRNA$name
selectVar(diablo.tcga, block = 'mRNA', comp = 2)$mRNA$name
selectVar(diablo.tcga, block = 'protein', comp = 2)$protein$name

## ----plot-diablo, message=FALSE, fig.cap='(ref:plot-diablo)'----
plotDiablo(diablo.tcga, ncomp = 2)
```
<p style="text-align: center;">**FIGURE: Multi block PLS-DA, diagnostic plot:** component 2, 95% confidence intervals are plotted. Numbers indicate correlation coefficients between the first components from each data set.</p>
<br>
<br>

```{r}
## ----diablo-plotindiv, message=FALSE, fig.cap='(ref:diablo-plotindiv)'----
plotIndiv(diablo.tcga, ind.names = FALSE, legend = TRUE, 
          title = 'TCGA, DIABLO comp 1 - 2')
```
<p style="text-align: center;">**FIGURE: Multi block PLS-DA, individual omes:** Check that extracted data sets can discriminate between samples: True.</p>
<br>
<br>

```{r}
plotIndiv(diablo.tcga, ind.names = FALSE, legend = TRUE, ellipse = TRUE, title = 'TCGA, DIABLO comp 1 - 2', block = 'average')
```
<p style="text-align: center;">**FIGURE: Multi block PLS-DA:** Main plot that includes all three data sets - with symbols.</p>
<br>
<br> 
 
```{r}
plotIndiv(diablo.tcga, ind.names = TRUE, legend = TRUE, 
          title = 'TCGA, DIABLO comp 1 - 2', block = 'average')
```
<p style="text-align: center;">**FIGURE: Multi block PLS-DA:** Main plot that includes all three data sets - with individual sample names.</p>
<br>
<br> 

### plotArrow
```{r}
## ----diablo-plotarrow, message=FALSE, fig.cap='(ref:diablo-plotarrow)'----
plotArrow(diablo.tcga, ind.names = FALSE, legend = TRUE, 
          title = 'TCGA, DIABLO comp 1 - 2')
```
<p style="text-align: center;">**FIGURE: arrow plot for Multi block PLS-DA:** Shows agreement between the three data sets. Some samples have a bit of variability between data sets.</p>
<br>
<br>

### plotVar
```{r}
## ----diablo-plotvar, message=FALSE, fig.cap='(ref:diablo-plotvar)'----
plotVar(diablo.tcga, var.names = FALSE, style = 'graphics', legend = TRUE, 
        pch = c(16, 17, 15), cex = c(2,2,2), 
        col = c('darkorchid', 'brown1', 'lightgreen'),
        title = 'TCGA, DIABLO comp 1 - 2')
```
<p style="text-align: center;">**FIGURE: circle plot for Multi block PLS-DA:** Shows correlation between variables.</p>
<br>
<br>

```{r}
## ----diablo-plotvar, message=FALSE, fig.cap='(ref:diablo-plotvar)'-----------
plotVar(diablo.tcga, var.names = TRUE, style = 'graphics', legend = TRUE,         pch = c(16, 17, 15), cex = c(1,1,1), 
        col = c('darkorchid', 'brown1', 'lightgreen'),
        title = 'TCGA, DIABLO comp 1 - 2')

```
<p style="text-align: center;">**FIGURE: circle plot for Multi block PLS-DA:** Shows correlation between variables - and names, which are overlapping unfortunately.</p>
<br>
<br>

### circosPlot
```{r}
## ----diablo-circos, message=FALSE, fig.cap='(ref:diablo-circos)'----
circosPlot(diablo.tcga, cutoff = 0.7, line = TRUE, 
           color.cor = c("chocolate3","grey20"), size.labels = 1.5)
```
<p style="text-align: center;">**FIGURE: circos plot for Multi block PLS-DA:** Plot represents the correlations between variables of different types, represented on the side quadrants..</p>
<br>
<br>

### cimDiablo
```{r, eval=FALSE}
## ----diablo-cim, message=FALSE, fig.width=10, fig.height=8, fig.cap='(ref:diablo-cim)'----
# FIGURE CAN BE OUT OF BONDS, MARGINS NEED TO BE ADJUSTED..
cimDiablo(diablo.tcga, color.blocks = c('darkorchid', 'brown1', 'lightgreen'),
          comp = 1, margin=c(8,20), legend.position = "right")
```
```{r}
# USE THIS CODE INSTEAD TO EXPORT HEATMAP
time<-format(Sys.time(),"%d-%m-%Y")
Title <- paste("Clustered Image Map for Multi block PLS-DA")
FileName <- paste(Title,time,".jpg")
jpeg(file=FileName, width = 2280, height = 1280, res = 210)
#
cimDiablo(diablo.tcga, color.blocks = c('darkorchid', 'brown1', 'lightgreen'), comp = 1, margin=c(8,20), legend.position = "right")
#
dev.off()
```
<p style="text-align: center;">**FIGURE: Clustered Image Map (CIM) for Multi block PLS-DA:** Shows correlation between variables - and names.</p>
<br>
<br>

### plotLoadings
```{r}
## ----diablo-loading, message=FALSE, fig.cap='(ref:diablo-loading)'----
plotLoadings(diablo.tcga, comp = 1, contrib = 'max', method = 'median')
```
<p style="text-align: center;">**FIGURE: SYMBIONT contributing variables to sparse PLS-DA:** comp 1.</p>
<br>
<br>

```{r}
## ----diablo-loading, message=FALSE, fig.cap='(ref:diablo-loading)'----
plotLoadings(diablo.tcga, comp = 2, contrib = 'max', method = 'median')
```
<p style="text-align: center;">**FIGURE: SYMBIONT contributing variables to sparse PLS-DA:** comp 2.</p>
<br>
<br>

```{r}
## variables selected for block LIPIDS on component 1 & 2
selectVar(diablo.tcga, block = 'miRNA', comp = 1)$miRNA$value
selectVar(diablo.tcga, block = 'miRNA', comp = 2)$miRNA$value

## variables selected for block METABOLITES on component 1 & 2
selectVar(diablo.tcga, block = 'mRNA', comp = 1)$metabolites$value
selectVar(diablo.tcga, block = 'mRNA', comp = 2)$metabolites$value

## variables selected for block PROTEOME on component 1 & 2
selectVar(diablo.tcga, block = 'protein', comp = 1)$protein$value
selectVar(diablo.tcga, block = 'protein', comp = 2)$protein$value
```


```{r}
## --------------------------------
# Performance with Majority vote
perf.diablo.tcga$MajorityVote.error.rate

## --------------------------------
# Performance with Weighted vote
perf.diablo.tcga$WeightedVote.error.rate

```
<br>
<br>


## Model performance and prediction
```{r}
# NOT COVERED HERE
```


# WORKING WITH OWN DATA
```{r OwnData, eval=FALSE}
#getwd()
#setwd("PATH/TO/FOLDER")

# REQUIRED FORMAT:
# -> Your samples in rows, with unique IDs
# -> Your data in columns, with short and unique names

# Load from csv file
data_1 <- read.csv("PATH/TO/FOLDER/file1.csv", row.names = 1, header = TRUE, sep = '\t')

data_2 <- read.csv("PATH/TO/FOLDER/file1.csv", row.names = 1, header = TRUE, sep = '\t')

data_3 <- read.csv("PATH/TO/FOLDER/file1.csv", row.names = 1, header = TRUE, sep = '\t')

# Reformat data to matrix
data_1 <- as.matrix(data_1)

data_2 <- as.matrix(data_2)

data_3 <- as.matrix(data_3)

# Generate list of the data sets
X <- list(data_1 = data_1, 
          data_2 = data_2,
          data_3 = data_3)
summary(X)

# Load Outcome file
data_meta <- read.csv("PATH/TO/FOLDER/MetaData.csv", header = TRUE, sep = '\t')

# Reformat Outcome file
Y_factor <- data_meta$YourFactor %>% as.factor()
summary(Y)

Y_scale <- data_meta$YourScale %>% as.numeric()
summary(Y_scale)

```
<br>
<br>


<!-- New page -->     
\pagebreak

# SESSION INFO
```{r}
sessionInfo()
```
